---
title: "MATH 216 Homework 2 Shiny App"
author: "Amanda Hotvedt"
output: html_document
runtime: shiny
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(ggplot2)
library(dplyr)
library(babynames)
library(ggplot2movies)
```


## Inputs and Outputs

You can embed Shiny inputs and outputs in your document. Outputs are automatically updated whenever inputs change.  This demonstrates how a standard R plot can be made interactive by wrapping it in the Shiny `renderPlot` function. The `selectInput` and `sliderInput` functions create the input widgets used to drive the plot.

```{r eruptions, echo=FALSE}

inputPanel(
  
  # Select genre
  radioButtons("Genre", "Select Genre:", c("Comedies"="Comedies", "Non-comedies"="Non-comedies"))
)

renderPlot({

movies2 <- movies %>% 
  mutate(Genre = ifelse(Comedy == 1, "Comedies", "Non-comedies")) %>% 
  filter(!is.na(budget)) %>% 
  filter(Genre == input$Genre)
  
  # Make a plot
  ggplot(data=movies2, aes(x=budget, y=rating)) + 
    geom_point() +
    geom_smooth() +
    labs(x = "Budget for Movie", y = "Movie Rating", title = "Movie Ratings with Respect to Budget")
  
})
```

The graph in the shiny app demonstrates that a higher budget is correlated with higher ratings for Non-comedies, but for Comedies it seems that ratings stay pretty flat with an increased budget.